Tulai

### 2023-09-20 paper/paper_tulai.qmd
stopping work to wait for updates from SS

```{r}
# load libraries
library(tidyverse)
library(here)
library(ggpmisc)
library(ggrepel)
library(ggbeeswarm)
library(cowplot)
```

@@

@@

```{r}
# Specify the exact columns want to keep
desired_columns <- c("TA", "depth", "area", "layer", "upper", "lower", 
                     "Cores (n)", "Core rejuvenations pieces (n)", 
                     "Blade (n)", "Flake (n)", "Bladelet (n)", 
                     "Retouched Tools (n)", "Utilized (n)", "Sickle Shine (n)",
                     "tool_type")  # Only keep this 'tool_type'

@@

# Generate the table
kable(summary_table_depth_area_layer, 
      caption = "Summary of lithics by Depth, Area, and Layer")

@@

# import table with depths that we have subdivided
depths_divided_tbl <- read_csv(here("data/Lookup Table - Sheet1.csv"))

# join with lithic data
tl_final %>% 
  left_join(depths_divided_tbl) %>% View

@@

library(tidyverse)
library(googlesheets4)

>>>>

```{r}
# load libraries
library(tidyverse)
library(here)
library(ggpmisc)
library(ggrepel)
library(ggbeeswarm)
library(cowplot)
library(knitr)
```

@@

summary_table_depth_area_layer_to_join <- 
  summary_table_depth_area_layer

@@

```{r}
# Specify the exact columns want to keep
desired_columns <-
  c(
    "TA",
    "depth",
    "area",
    "layer",
    "upper",
    "lower",
    "Cores (n)",
    "Core rejuvenations pieces (n)",
    "Blade (n)",
    "Flake (n)",
    "Bladelet (n)",
    "Retouched Tools (n)",
    "Utilized (n)",
    "Sickle Shine (n)",
    "tool_type"
  )  # Only keep this 'tool_type'

@@

@@

# import table with depths that we have subdivided
depths_divided_tbl <- 
  read_csv(here("data/Lookup Table - Sheet1.csv")) %>% 
  mutate(division_id = rep(c("a", "b"),
                           nrow(.)/2))

# google sheet has 42 rows, and cols for 
# area, layer, level, depth. What is the equivalent above? tp1_c_3_a

# This 'depths_divided_tbl' needs more information, for example, some depth ranges

# join with lithic data that 
summary_table_depth_area_layer_to_join %>% 
  left_join(depths_divided_tbl) %>% 
  mutate(label = paste(area, 
                       layer, 
                       # level, # need this
                       division_id,
                       sep = "_")) %>% View

@@

library(googlesheets4)
